Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2022-06-08 paper/ms.tex
Small updates

\newcommand{\Nbody}{$N$-body}
\newcommand{\Msun}{\ensuremath{M_{\odot}}}

@@

\item [Acknowledgements] We would like to thank Greg~L. Bryan, Neal~J. Evans,
Drummond~B. Fielding, Keith Hawkins, Jason~A.~S. Hunt, Sarah~M.~R. Jeffreson,
Kathryn~V. Johnston, Peter~M.~W. Kalberla, Jürgen Kerp, Julio~F. Navarro,
Joshua~S. Speagle, Martin~D. Weinberg, and Yanfei Zou for helpful discussions.
A.B. would like to thank Todd Phillips for helpful discussions. Some
computations in this paper were run on the FASRC Cannon cluster supported by
the FAS Division of Science Research Computing Group at Harvard University.
Resources supporting this work were also provided by the NASA High-End
Computing (HEC) Program through the NASA Advanced Supercomputing (NAS)
Division at Ames Research Center. A.B. was supported by the Future
Investigators in NASA Earth and Space Science and Technology (FINESST) award
number 80NSSC20K1536 during the completion of this work. L.H. funding. E.D.
funding. C.C. funding. J.Q. acknowledges support from NSF grant
AST-2008490. L.V.S. funding. P.T. acknowledges support from NSF grant
AST-1909933, AST-2008490, and NASA ATP Grant 80NSSC20K0502. M.V. acknowledges
support through NASA ATP 19-ATP19-0019, 19-ATP19-0020, 19-ATP19-0167, and NSF
grants AST-1814053, AST-1814259, AST-1909831, AST-2007355 and AST-2107724.

@@

\begin{figure*}[t!]%
\centering
\includegraphics[width=18cm]{fig/fig-bar.pdf}
\caption{\textbf{Disk decomposition into the bar and unbarred disk.} This
procedure is based on ref.\cite{2016MNRAS.463.1952P} The \textit{left panel}
shows a surface density projection through the stellar component of the
\Nbody{} simulation (disk and bulge). The \textit{middle panel} shows the
component of the disk identified as being trapped in the bar while the
\textit{right panel} shows the component of the disk identified as not being
trapped in the bar. The fact that the untrapped stars form a roughly
axisymmetric structure indicates our bar decomposition is sufficiently
accurate.}
\label{fig:decomp}
\end{figure*}

>>>>

\newcommand{\Nbody}{$N$-body}
\newcommand{\SMUGGLE}{SMUGGLE}
\newcommand{\Msun}{\ensuremath{M_{\odot}}}

@@

\item [Acknowledgements] We would like to thank Greg~L. Bryan, Neal~J. Evans,
Drummond~B. Fielding, Keith Hawkins, Jason~A.~S. Hunt, Sarah~M.~R. Jeffreson,
Kathryn~V. Johnston, Peter~M.~W. Kalberla, Jürgen Kerp, Julio~F. Navarro,
Joshua~S. Speagle, Martin~D. Weinberg, and Yanfei Zou for helpful discussions.
A.B. would like to thank Todd Phillips for helpful discussions. Some
computations in this paper were run on the FASRC Cannon cluster supported by
the FAS Division of Science Research Computing Group at Harvard University.
Resources supporting this work were also provided by the NASA High-End
Computing (HEC) Program through the NASA Advanced Supercomputing (NAS)
Division at Ames Research Center. A.B. was supported by the Future
Investigators in NASA Earth and Space Science and Technology (FINESST) award
number 80NSSC20K1536 during the completion of this work. L.H. funding. E.D.
funding. J.Q. acknowledges support from NSF grant
AST-2008490. L.V.S. funding. P.T. acknowledges support from NSF grant
AST-1909933, AST-2008490, and NASA ATP Grant 80NSSC20K0502. M.V. acknowledges
support through NASA ATP 19-ATP19-0019, 19-ATP19-0020, 19-ATP19-0167, and NSF
grants AST-1814053, AST-1814259, AST-1909831, AST-2007355 and AST-2107724.

@@

\begin{figure*}[t!]%
\centering
\includegraphics[width=18cm]{fig/fig-bar.pdf}
\caption{\textbf{Disk decomposition into the barred and unbarred disk.} This
procedure is based on ref.\cite{2016MNRAS.463.1952P} The \textit{left panel}
shows a face-on surface density projection through the stellar component of the
\SMUGGLE{} simulation (disk and bulge) at $t=1\,\textrm{Gyr}$. The \textit{middle panel} shows the
component of the disk identified as being trapped in the bar while the
\textit{right panel} shows the component of the disk identified as not being
trapped in the bar. The fact that the untrapped stars form a roughly
axisymmetric structure indicates our bar decomposition is sufficiently
accurate.}
\label{fig:decomp}
\end{figure*}
